
Loading libraries
```{r}
library(readxl)
library(tidyverse)
library(ggplot2)
library(scales)
library(writexl)
library(tibble)
```

Downloading salary database
```{r}
df <- read_excel("salary_2013-2024.xlsx")
View(df)
```

Cleaning the salary data
```{r}
df$Salary <- as.numeric(gsub("[$,]", "", df$Salary))
```

Viewing the updated data
```{r}
View(df)
```

Creating minimum salary column
```{r}
min_salary <- c(490180, 507336, 525093, 543471, 815615, 831927, 898310, 898310, 925258, 953012, 1119563)
```

Creating a season summary of salaries
```{r}
salary_seasons <- df %>%
  group_by(Year) %>%
  summarise(players = n(), avg_salary = mean(Salary), median_salary = median(Salary), most_paid = max(Salary), min_paid = min(Salary))

salary_seasons <- salary_seasons %>%
  add_column(min_salary = min_salary)
View(salary_seasons)
```

Saving databases
```{r}
#write_xlsx(salary_seasons, "salary_seasons.xlsx")
#write_xlsx(df, "salary_2013-2024_cleaned.xlsx")
```

Downloading cleaned data without players under mininum salary
```{r}
df2 <- read_excel("salary_2013-2024_cleaned.xlsx")
View(df2)
```

Creating a season summary of salaries
```{r}
salary_seasons2 <- df2 %>%
  group_by(Year) %>%
  summarise(players = n(), avg_salary = mean(Salary), median_salary = median(Salary), most_paid = max(Salary), min_paid = min(Salary))

salary_seasons2 <- salary_seasons2 %>%
  add_column(min_salary = min_salary)
View(salary_seasons2)
```

Ploting salary_seasons
```{r}
ggplot(salary_seasons2, aes(x = Year, y = avg_salary))  +
  geom_line(color="#69b3a2", size=2)
```

Saving databases
```{r}
#write_xlsx(salary_seasons2, "salary_seasons2.xlsx")
#write_xlsx(df, "salary_2013-2024_cleaned.xlsx")
```

Count unique players
```{r}
all_players <- distinct(df2,Player)
View(all_players)
```

Save players list
```{r}
#write_csv(all_players, "All_players.csv")
```

Salary for 2023-24 season
```{r}
salary_2024 <- df2 %>%
  filter(Year == 2024)
```

Distribution of NBA salary for 2023-24 season
```{r}
salary_histogram <- ggplot(salary_2024, aes(x = Salary)) +
  geom_histogram(binwidth = 1000000, color = "white", fill = "#0072B2") + 
  labs(title = "Distribution of NBA Player Salaries for 2023-24 season", x = "Salary", y = "Number of Players") + 
  scale_x_continuous(labels = scales::dollar_format(prefix = "$"), breaks = seq(0, max(salary_2024$Salary), by = 1e7)) + 
  theme(plot.title = element_text(hjust = 0.5))

salary_histogram
```


